FocalGstar

### 2017-06-15 analysis.Rmd
new wmatrix images

```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for(ws in wsizes) {
  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  plot_weight_matrix(w)
}
```

>>>>

```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for(ws in wsizes) {
  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  plot_weight_matrix(w, show.minmax = FALSE)
}
```
